---
title: "homework2"
format: pdf
editor: visual
author:
  name: Aryan Nagaradona
---

# Packages

## Question 1

```{r}
eval = FALSE
install.packages("aRtsy")
```

Install.packages downloads the specific package locally to your computer for usage of the functions. Library allows you to access the specific package at any given time as long as it was downloaded onto the computer previously. Thus, allowing for functions to be masked accordingly with packages based on the developers needs.

## Question 2

```{r}
library(aRtsy)
```

The Collatz conjecture equation is a unsolved math problem that asks if repeating two rules will bring two positive whole numbers back down to 1. Specifically if you have a even number n perform the calculation (n/2) and if the number is odd perform the calculation (3n + 1) will it always go back to 1.

The Collatz conjecture is defined as if if $n \%\% 2 = 0$ then $n \gets n/2$ else $n \gets 3n+1$, and the conjecture states that iterating $f$ on any positive integer $n$ will eventually reach $1$.

## Question 3

#### Part A

```{r}
library(aRtsy)
canvas_collatz(
  colors = c("blue"),
  n = 10
)
```

The function canvas_collatz() takes an empty canvas and draws lines on them based on the collatz conjecture and the parameters within the function. In this case, since colors is set to blue and n = 10 the output is 10 blue lines using a random starting integer for the collatz conjecture.

#### Part B

-You get a different output every time because the starting point is a random positive integer n for the collatz conjecture. Thus, the only controlled variables is the number of lines and the color of the lines.

-This would be difficult to input into a .qmd file because quarto documents are not designed for varying output changes and are rather meant for rendering reproducible content.

-The set seed function allows for the starting integer for the collatz conjecture to be set. Resulting in the same output everytime you run the code making it perfect for a .qmd document.

```{r}
library(aRtsy)
set.seed(10)
canvas_collatz(
  colors = c("blue"), 
  n = 10)
```

## Question 4

```{r}
canvas_collatz(
  colors = c("blue"),
  n = 1:20
)
```

This code chunk is passing a sequence vector of 1 to 20. While the previous code chunk passed a integer of 10. The result is a visualized path for each integer 1 through 20 in the collatz sequence producing the same result every time. In comparison to 10 random integer starting values for the collatz sequence being drawn.

Including set.seed(1) into the code would be unnecessary as the output would remain the same since the starting point is already set in the original code with the vector
